\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 concepts.tex
updates on europa.tex for Javier

\item[\textbf{Rules}] In order for a plan to be valid, it must comply
  with all rules pertinent to the relevant application domain. Rules
  govern the internal and external relationships of a token. For
  example, consider a parameterized action
  \texttt{Go(origin,destination)} which describes a Shopping Agent
  traveling from one location (\textit{origin}) to another
  (\textit{destination}). The parameters are instantiated on a token
  as variables whose domain of values is the set of all possible
  locations in a given problem. A rule governing an internal
  relationship among token variables might stipulate that a transition
  must involve a change in location. This can be expressed as a
  constraint on the definition of a predicate of the form:
  \textit{origin != destination}. A further stipulation could be that
  the agent must be located at \textit{origin} before travel can occur
  and the agent must be located at \textit{destination} when travel is
  completed. This is an example of a rule governing an external
  relationship among tokens. It specifies a requirement that tokens of
  the predicate \texttt{At} that represent the location state for the
  Shopping Agent precede and succeed tokens of the predicate
  \texttt{Go} that represents traveling.

@@

  Fig. \ref{fig:europapr:rules} illustrates the entities and relations
  involved in specifying such a rule on a \texttt{Go} action. The
  token on which the rule applies (\texttt{Go}) is referred to as the
  \emph{master}. Each \texttt{At} and \texttt{Going} token required by
  the master is referred to as a \emph{slave}.  Application of a rule
  on a token can thus cause slave tokens, variables and constraints to
  be introduced.  The capability of a domain rule to cause a slave
  token to be created is a key vehicle through which planning
  occurs. Semantically, a rule imposes a requirement for supporting
  (slave) tokens to be in the plan in order for the master token to be
  valid.

>>>>

\item[\textbf{Rules}] In order for a plan to be valid, it must comply
  with all rules pertinent to the relevant application domain. Rules
  govern the internal and external relationships of a token. For
  example, consider a parameterized action
  \texttt{Go(origin,destination)} which describes a Shopping Agent
  traveling from one location (\textit{origin}) to another
  (\textit{destination}). The parameters are instantiated on a token
  as variables whose domain of values is the set of all possible
  locations in a given problem. A rule governing an internal
  relationship among token variables might stipulate that a transition
  must involve a change in location. This can be expressed as a
  constraint on the definition of a predicate of the form:
  \textit{origin != destination}. A further stipulation could be that
  the agent must be located at \textit{origin} before travel can occur
  and the agent must be located at \textit{destination} when travel is
  completed. This is an example of a rule governing an external
  relationship among tokens. It specifies a requirement that tokens of
  the predicate \texttt{At} that represent the location state for the
  Shopping Agent precede and succeed tokens of the predicate
  \texttt{Go} that represents traveling. Fig. \ref{fig:europapr:rules}
  illustrates the entities and relations involved in specifying such a
  rule on a \texttt{Go} action. The token on which the rule applies
  (\texttt{Go}) is referred to as the \emph{master}. Each \texttt{At}
  and \texttt{Going} token required by the master is referred to as a
  \emph{slave}.  Application of a rule on a token can thus cause slave
  tokens, variables and constraints to be introduced.  The capability
  of a domain rule to cause a slave token to be created is a key
  vehicle through which planning occurs. Semantically, a rule imposes
  a requirement for supporting (slave) tokens to be in the plan in
  order for the master token to be valid.

@@

### 2012-02-24 constraints-table.tex
updates on europa.tex for Javier

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.2}%{0.99}
  \begin{tabular}{|l|l|p{8cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    distanceSquares& distanceSquares(a,b,c)& c = sqrt(a+b) if a and b are singleton& Numeric intervals\\
    \hline
    calcDistance&calcDistance(a,b,c,d,e)& a is Euclidean distance between points (b,c) and (d,e)& Numeric intervals\\
    \hline
    sin& sin(a,b)& a = sin(b)& Numeric intervals\\
    \hline
    allDiff& allDiff(a,b,\ldots)& Restrict all domains so the intersection of any pair of domains is empty& Comparable\\
    \hline
    EqualMaximum& EqualMax(a,b,\ldots)& a = max(b,\ldots)& Numeric\\
    \hline
    EqualMinimum& EqualMin(a,b,\ldots)& a = min(b,\ldots)& Numeric\\
    \hline
    CountZeros& CountZeros(a,b,\ldots)& a is the count of the rest that can be zero& Numeric\\
    \hline
    CountNonZeros& CountNonZeros(a,b,\ldots)& a is the count of the rest that can be non-zero& Numeric\\
    \hline
    diffSquare& diffSquare(a,b,\ldots)& c = (a - b)$^2$ if a and b are singleton& Numeric intervals\\
    \hline
    card& card(a,b,\ldots)& a must be greater than or equal the count of the other variables that are true& Numeric\\
    \hline
  \end{tabular}
  \caption{\small Calculation Constraints: These constraints enforce that one variable (usually a) is constrained by a calculation done on the remaining variables.}
  \label{tab:calconst}
\end{table*}

@@

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{8cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    subsetOf& subsetOf(a,b)& a is a subset of b& Comparable\\
    \hline
    memberImply& memberImply(a,b,c,d)& If a is a subset of b, then require that c is a subset of d& a and b comparable, c and d comparable\\
    \hline
    Lock& Lock(a,b)& Restrict a's domain to be contained in b's domain& Comparable\\
    \hline
  \end{tabular}
  \caption{\small Set Constraints: These constraints are likely to be used for set comparisons etc. Note, however, that many of the other constraints could be used for sets (\ie Comparable variables) just as these constraints could be applied to numeric domains as well.}
  \label{tab:setconst}
\end{table*}

@@

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{5cm}|p{3.5cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    commonAncestor& commonAncestor(a,b,c)& a and b must be contained by the same object in c (or by c itself)& a, b and c are all objects\\
    \hline
    hasAncestor& hasAncestor(a,b)& a must be contained by some object in b& a and b are objects\\
    \hline
  \end{tabular}
  \caption{\small Object Hierarchy Constraints: These constraints are imposed on objects and tokens. These constraints are used to assert which object one or more tokens is contained by. Most often, the commonAncestor constraint is used to subgoal across timelines which must share a contained object in common.}
  \label{tab:objhierarchy}
\end{table*}

@@

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{10cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    UNARY& NA& Restrict a variable's domain; given a variable and a domain, intersect them. Note that this constraints is only available internally and not exposed in NDDL& Anything\\
    \hline
    or& or(a,b\ldots)& At least one of the variables must be true& Numeric\\
    \hline
    absVal& absVal(a,b)& a.lb $\geq$ 0, a.ub = max(abs(b.lb)), b.lb $\geq$ -a.lb, b.ub $\leq$ a.ub& Numeric\\
    \hline
  \end{tabular}
 \caption{\small Miscellaneous Constraints}
  \label{tab:misc}
\end{table*}

>>>>

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{7cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    distanceSquares& distanceSquares(a,b,c)& c = sqrt(a+b) if a and b are singleton& Numeric intervals\\
    \hline
    calcDistance&calcDistance(a,b,c,d,e)& a is Euclidean distance between points (b,c) and (d,e)& Numeric intervals\\
    \hline
    sin& sin(a,b)& a = sin(b)& Numeric intervals\\
    \hline
    allDiff& allDiff(a,b,\ldots)& Restrict all domains so the intersection of any pair of domains is empty& Comparable\\
    \hline
    EqualMaximum& EqualMax(a,b,\ldots)& a = max(b,\ldots)& Numeric\\
    \hline
    EqualMinimum& EqualMin(a,b,\ldots)& a = min(b,\ldots)& Numeric\\
    \hline
    CountZeros& CountZeros(a,b,\ldots)& a is the count of the rest that can be zero& Numeric\\
    \hline
    CountNonZeros& CountNonZeros(a,b,\ldots)& a is the count of the rest that can be non-zero& Numeric\\
    \hline
    diffSquare& diffSquare(a,b,\ldots)& c = (a - b)$^2$ if a and b are singleton& Numeric intervals\\
    \hline
    card& card(a,b,\ldots)& a must be greater than or equal the count of the other variables that are true& Numeric\\
    \hline
  \end{tabular}
  \caption{\small Calculation Constraints: These constraints enforce that one variable (usually $a$) is constrained by a calculation done on the remaining variables.}
  \label{tab:calconst}
\end{table*}

@@

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{7.5cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    subsetOf& subsetOf(a,b)& a is a subset of b& Comparable\\
    \hline
    memberImply& memberImply(a,b,c,d)& If a is a subset of b, then require that c is a subset of d& a and b comparable, c and d comparable\\
    \hline
    Lock& Lock(a,b)& Restrict a's domain to be contained in b's domain& Comparable\\
    \hline
  \end{tabular}
  \caption{\small Set Constraints: These constraints are likely to be used for set comparisons etc. Note, however, that many of the other constraints could be used for sets (\ie Comparable variables) just as these constraints could be applied to numeric domains as well.}
  \label{tab:setconst}
\end{table*}

@@

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{7cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    commonAncestor& commonAncestor(a,b,c)& a and b must be contained by the same object in c (or by c itself)& a, b and c are all objects\\
    \hline
    hasAncestor& hasAncestor(a,b)& a must be contained by some object in b& a and b are objects\\
    \hline
  \end{tabular}
  \caption{\small Object Hierarchy Constraints: These constraints are imposed on objects and tokens. These constraints are used to assert which object one or more tokens is contained by. Most often, the commonAncestor constraint is used to subgoal across timelines which must share a contained object in common.}
  \label{tab:objhierarchy}
\end{table*}

@@

\begin{table*}[ht]
  \centering
  \renewcommand{\arraystretch}{1.0}%{0.99}
  \begin{tabular}{|l|l|p{9.5cm}|p{3cm}|}
    \hline
    \textbf{Constraint}& \textbf{Syntax}& \textbf{Description}& \textbf{Variable Types}\\
    \hline
    UNARY& NA& Restrict a variable's domain; given a variable and a domain, intersect them. Note that this constraints is only available internally and not exposed in NDDL& Anything\\
    \hline
    or& or(a,b\ldots)& At least one of the variables must be true& Numeric\\
    \hline
    absVal& absVal(a,b)& a.lb $\geq$ 0, a.ub = max(abs(b.lb)), b.lb $\geq$ -a.lb, b.ub $\leq$ a.ub& Numeric\\
    \hline
  \end{tabular}
 \caption{\small Miscellaneous Constraints}
  \label{tab:misc}
\end{table*}

### 2012-02-24 europa-basics.tex
updates on europa.tex for Javier

\paragraph{} {\em Constraint Satisfaction}: A canonical problem in
dealing with constraints is the $N$-Queens problem in which chess queens
must be placed on an  $N \times N$ chessboard so no queens attack the other. % Fig.
% \ref{fig:nqueens-1} shows an example of a random positioning of queens
% on a  $N$x$N$ chessboard. Queens in violation of the non-attack constraint
% are highlighted in red.
% \begin{figure} \centering
%   \includegraphics[scale=0.35]{figs/Example-NQueens0.jpg}
%   \caption{\small N-Queens problem. Queens in violation of the
%     non-attack constraint are highlighted in red.}
% \label{fig:nqueens-1}
% \vskip+0.1cm
% \end{figure}
If we define $N$x$N$ variables Q$_{rc}$, $r \in [1,N]$, $c \in [1,N]$,
Q$_{rc} = 1$ if cell $r,c$ in the chessboard is occupied by a Queen,
$0$ otherwise. Then the following constraints need to be satisfied:

@@

A set of constraints and variables that describe a problem domain are
typically represented as a \emph{Constraint Network}, where the
variables are nodes and constraints are arcs between the variables. A
pair of variables $x \& y$ is said to be \emph{arc consistent} if for
every value in $x$'s domain, there is a value in $y$'s domain that is
consistent with all the constraints that connect $x$ and $y$.  A naive
approach to ensuring arc consistency consists of cycling through all
the variable pairs and performing constraint propagation until there
are no variable domain changes. The \texttt{AC-3} algorithm
\cite{mackworth77}, a popular implementation, improves over the naive
approach by ignoring constraints whose variables were not affected
since the last iteration. Fig. \ref{fig:constraintnet} shows a set of
constraints on $3$ variables ($x$, $y$ and $z$) represented as a
constraint network, and their domains before arc consistency is
enforced.  After the \texttt{AC-3} algorithm is executed, the domains
for the variables would be pruned to x=$\{2$\}, y=$\{2$\}, z=$\{2$\}.

>>>>

\paragraph{} {\em Constraint Satisfaction}: A canonical problem in
dealing with constraints is the $N$-Queens problem in which chess queens
must be placed on an  $N \times N$ chessboard so no queens attack the other. % Fig.
% \ref{fig:nqueens-1} shows an example of a random positioning of queens
% on a  $N$x$N$ chessboard. Queens in violation of the non-attack constraint
% are highlighted in red.
% \begin{figure} \centering
%   \includegraphics[scale=0.35]{figs/Example-NQueens0.jpg}
%   \caption{\small N-Queens problem. Queens in violation of the
%     non-attack constraint are highlighted in red.}
% \label{fig:nqueens-1}
% \vskip+0.1cm
% \end{figure}
If we define $N \times N$ variables Q$_{rc}$, $r \in [1,N]$, $c \in
[1,N]$, Q$_{rc} = 1$ if cell $r,c$ in the chessboard is occupied by a
Queen, $0$ otherwise. Then the following constraints need to be
satisfied:

@@

A set of constraints and variables that describe a problem domain are
typically represented as a \emph{Constraint Network}, where the
variables are nodes and constraints are arcs between the variables. A
pair of variables $x$ and $y$ is said to be \emph{arc consistent} if
for every value in $x$'s domain, there is a value in $y$'s domain that
is consistent with all the constraints that connect $x$ and $y$.  A
naive approach to ensuring arc consistency consists of cycling through
all the variable pairs and performing constraint propagation until
there are no variable domain changes. The \texttt{AC-3} algorithm
\cite{mackworth77}, a popular implementation, improves over the naive
approach by ignoring constraints whose variables were not affected
since the last iteration. Fig. \ref{fig:constraintnet} shows a set of
constraints on $3$ variables ($x$, $y$ and $z$) represented as a
constraint network, and their domains before arc consistency is
enforced.  After the \texttt{AC-3} algorithm is executed, the domains
for the variables would be pruned to x=$\{2$\}, y=$\{2$\}, z=$\{2$\}.
